Quantile Regressions via Method of Moments with multiple fixed effects

### 2023-11-07 article/article.tex
q(\tau)
q(\tau)

Quantile regression (QR), introduced by \citet{koenkerbasset1978}, is an
estimation strategy used for modeling the relationships between
explanatory variables X and the conditional quantiles of the dependent
variable \(q_\tau (y|x)\). Using QR one can obtain richer
characterizations of the relationships between dependent and independent
variables, by accounting for otherwise unobserved heterogeneity.

A relatively recent development in the literature has focused on
extending quantile regressions analysis to include individual fixed
effects in the framework of panel data. However, as described in
\citet{neymanscott1948}, and \citet{lancaster2000}, when individual
fixed effects are included in quantile regression analysis it generates
an incident parameter problem. While many strategies have been proposed
for estimating this type of model (see \citet{galvao2017quantile} for a
brief review), neither has become standard because of their restrictive
assumptions in regards to the individual effects, the computational
complexity, and implementation.

More recently, \citet{mss2019} (MSS hereafter) proposed a methodology
based on a conditional location-scale model similar to the one described
in \citet{he1997} and \citet{zhao2000}, for the estimation of quantile
regressions models for panel data via a method of moments. This method
allows individual fixed effects allowing to have heterogeneous effects
on the entire conditional distribution of the outcome, rather
constraining their effect to be a location shift only as in
\citet{canay2011}, \citet{koenker2004}, and \citet{lancaster2000}.

@@

The rest of the paper is restructured as follows. Section 2 presents the
basic setup of the location-Scale model described in \citet{he1997} and
\citet{zhao2000}, tying the relationship between the standard quantile
regression model, and the location and scale model. It also revisits MSS
methodology, proposing alternative estimators for the standard errors
based on the properties of GMM estimators and the empirical influence
functions. It also shows that FWL theorem can be used to control for
multiple fixed effects. Section 3 presents the results of a small
simulation study and Section 4 illustrates the application of the
proposed methods with two empirical examples. Seccion 5 concludes.

@@

Quantile regressions are used to identify relationships between the
explanatory variables \(x\) and the conditional quantiles of the
dependent variable \(Q(y|\tau,X)\). This relationship is commonly
assumed to follow a linear functional form:

\begin{equation}\phantomsection\label{eq-eq1}{q(Y|X,\tau) =X\beta(\tau)
}\end{equation}

This allows for nonlinearities in the effect of \(X\) on \(Y\) across
all values of \(\tau\). This formulation can also be related to a random
coefficient model, where all coefficients are assumed to be some
nonlinear function of \(\tau\), where \(\tau\) follows a random uniform
distribution.

@@

\begin{equation}\phantomsection\label{eq-eq2}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
}\end{equation}

Here, the location parameters \(\beta\) are typically identified using a
linear regression model (as in \citet{mss2019}), or a median regression
(as in \citet{melly2005}), and the scale parameters \(\gamma(\tau)\) can
be estimated using standard approaches.

@@

\begin{equation}\phantomsection\label{eq-eq5}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
}\end{equation}

In this setup, the traditional quantile coefficients are identified as
the location model coefficients, plus the scale model coefficients
moderated by the \(\tau_{th}\) unconditional quantile of the
standardized error \(\varepsilon\).

\begin{equation}\phantomsection\label{eq-eq6}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
}\end{equation}

While this specification imposes a strong assumption on the DGP, it has
two advantages over the standard quantile regression model. First,
because the location and scale model can be identified globally, with
only a single paramater (\(q(\varepsilon|\tau)\)) requiring local
estimation, this estimation approach would be more efficient than the
standard quantile regression model (\citet{zhao2000}). Second, under the
assumption that \(X\gamma\) is strictly possitive, the model would
produce quantile coefficients that do not cross.

Following MSS, the quantile regression model defined by
Equation~\ref{eq-eq5} can be estimated using a method of moments
approach. And while its possible to identify all coefficients
(\(\beta,\gamma, q(\varepsilon|\tau)\)) simultaneously, we describe and
use the implementation approach advocated by MSS which identifies each
set of coefficients separately.

First, the location model can be estimated using a standard linear
regression model, where the dependent variable is the outcome \(Y\), and
the independent variables are the explanatory variables \(X\) (including
a constant) with an error \(u\), which is by definition heteroskedastic.
In this case, the location model coefficients are identified under the
following condition:

@@

\begin{equation}\phantomsection\label{eq-eq8}{\begin{aligned}
  |\nu_i| &=x_i'\gamma+\omega_i \\
  E\big[ x_i \omega_i \big] &=0 \\
  E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
  \end{aligned}
}\end{equation}

Thurd, given the location and scale coefficients, the \(\tau_{th}\)
quantile of the error \(\varepsilon\) can be estimated using the
following condition:

\begin{equation}\phantomsection\label{eq-eq9}{\begin{aligned}
  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
  \end{aligned}
}\end{equation}

Where one identifies the quantile of the error \(\varepsilon\) using
standardized errors \(\frac{y_i-x_i'\beta}{x_i'\gamma}\), or by finding
the values that identify the overall quantile coefficients
\(\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)\). Afterwords, the
conditional quantile coefficients is simply defined as the combination
of the location and scale coefficients.

@@

\begin{equation}\phantomsection\label{eq-eq10}{\begin{aligned}
  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
  &=E[h_{3,i}]=0 
  \end{aligned}
}\end{equation}

@@

Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\varepsilon|\tau)' ]'\) the set
of coefficients that are identified by the modement conditions in
Equation~\ref{eq-eq10}, a just identified model. And the function
\(h_i\) is a vector function that stacks all the moments at the
individual level described in Equation~\ref{eq-eq10}. Then
\(\hat\theta\) follows a normal distribution with mean \(\theta\) and
variance-covariance matrix \(V(\theta)\) that is estimated as:

@@

In this framework, the quantile regression coefficients, a combination
of the location-scale-quantile estimates, will follow a normal
distribution with mean \(\beta(\tau) = \beta+q(\varepsilon|\tau)\gamma\)
and variance-covariance matrix equal to:

@@

\begin{equation}\phantomsection\label{eq-eqqtile}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
}\end{equation}

@@

\begin{equation}\phantomsection\label{eq-ifs}{\begin{aligned}
\lambda_i(\theta)&=
  \begin{bmatrix}
  \lambda_{i}(\beta) \\
  \lambda_{i}(\gamma) \\
  \lambda_{i}(q(\varepsilon|\tau)) 
  \end{bmatrix} \\
\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
\lambda_{i}(q(\varepsilon|\tau))&=\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\varepsilon|\tau))}
- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
-  q(\varepsilon|\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
}\end{equation}

@@

\[\hat{V}_{robust}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\varepsilon|\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\varepsilon|\tau))' \\
 \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\varepsilon|\tau))' \\
 \sum \lambda_i(q(\varepsilon|\tau) \lambda_i(\beta)' & \sum \lambda_i(q(\varepsilon|\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\varepsilon|\tau)) \lambda_i(q(\varepsilon|\tau))' 
  \end{pmatrix}
\]

@@

\[\hat{V}_{clustered}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\varepsilon|\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
  \end{pmatrix}
\]

@@

\[\begin{aligned}
\tilde \lambda_{1,i}&=\tilde \lambda_{2,i}=N (X'X)^{-1}  x_i ( x_i'\gamma) \\  
\tilde \lambda_{3,i}&=x_i' \gamma  \\
\tilde \psi_1 &= \varepsilon_i \\
\tilde \psi_2 &= \tilde \varepsilon_i -1 \\
\tilde \psi_3 &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\varepsilon|\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
-  q(\varepsilon|\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
\]

@@

\[\hat{V}_{gls}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\varepsilon|\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{11} \hat\Omega_{13} \\
 \hat\sigma_{21} \hat\Omega_{21} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{21} \hat\Omega_{23} \\
 \hat\sigma_{31} \hat\Omega_{31} & \hat\sigma_{32} \hat\Omega_{32} & \hat\sigma_{33} \hat\Omega_{33}
  \end{pmatrix}
\]

@@

\[\begin{aligned}
\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \phi_{i} \phi_{j}
\end{aligned}
\]

@@

Similar to the findings in MSS, we find that the estimator presents a
bias when the sample is small (\(N=500\)), but this bias shrinks as the
sample sizes increases. As MSS describes, the bias seems to be
proportional to the sample size, or more precisely to \(N/N_{g1}\) and
\(N/N_{g2}\), where \(N_{g1}\) and \(N_{g2}\) are the average number of
observations per group. Interestingly, the bias-corrected estimator
presents an almost zero bias, even when the samples are is small (about
10 observations per sub-group). Also replicating the results of MSS,
despite bias reduction obtained using the JKC estimator, the standard
errors and mean squared error (MSE) are larger than without correction.

\begin{table}

\caption{\label{tbl-sim1}Bias, Simulated Standard error, and Mean
Squared Error}

\begin{minipage}[t]{0.50\linewidth}

\begin{longtable}[]{@{}lccc@{}}
\toprule\noalign{}
N = 500 & Bias & Sim SE & MSE \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
q25 & & & \\
~mmqreg & 0.104 & 0.247 & 0.072 \\
~jkc & 0.008 & 0.297 & 0.088 \\
q75 & & & \\
~mmqreg & -0.091 & 0.251 & 0.071 \\
~jkc & 0.002 & 0.303 & 0.092 \\
\end{longtable}

\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

\begin{longtable}[]{@{}lccc@{}}
\toprule\noalign{}
N = 1000 & Bias & Sim SE & MSE \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
q25 & & & \\
~mmqreg & 0.050 & 0.173 & 0.032 \\
~jkc & -0.001 & 0.191 & 0.036 \\
q75 & & & \\
~mmqreg & -0.044 & 0.176 & 0.033 \\
~jkc & 0.006 & 0.195 & 0.038 \\
\end{longtable}

\end{minipage}%
\newline
\begin{minipage}[t]{0.50\linewidth}

\begin{longtable}[]{@{}lccc@{}}
\toprule\noalign{}
N = 1000 & Bias & Sim SE & MSE \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
q25 & & & \\
~mmqreg & 0.025 & 0.122 & 0.016 \\
~jkc & 0.003 & 0.129 & 0.017 \\
q75 & & & \\
~mmqreg & -0.023 & 0.124 & 0.016 \\
~jkc & 0.001 & 0.131 & 0.017 \\
\end{longtable}

\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

\begin{longtable}[]{@{}lccc@{}}
\toprule\noalign{}
N = 2000 & Bias & Sim SE & MSE \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
q25 & & & \\
~mmqreg & 0.012 & 0.087 & 0.008 \\
~jkc & 0.000 & 0.089 & 0.008 \\
q75 & & & \\
~mmqreg & -0.011 & 0.087 & 0.008 \\
~jkc & 0.000 & 0.089 & 0.008 \\
\end{longtable}

\end{minipage}%

\end{table}%

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
\caption{Heteroskedasticity misspecification and clustered
errors}\label{tbl-sim2}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Het:q25
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Het:q75
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Clust:q25
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Clust:q75
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Het:q25
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Het:q75
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Clust:q25
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Clust:q75
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Coefficient & 0.550 & 1.442 & 0.775 & 1.229 \\
SIM\_SE & 0.154 & 0.155 & 0.109 & 0.107 \\
GLS\_SE & 0.476 & 0.451 & 0.288 & 0.221 \\
Robust & 0.140 & 0.139 & 0.087 & 0.088 \\
Cluster & & & 0.097 & 0.097 \\
\end{longtable}

@@

  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1099}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}@{}}

@@

\[q(y|\tau,x) = x'(\beta + q(\varepsilon |\tau) \times \gamma)\]

This model is identified under the following conditions:

>>>>

Quantile regression (QR), introduced by \citet{koenkerbasset1978}, is an
estimation strategy used for modeling the relationships between
explanatory variables X and the conditional quantiles of the dependent
variable \(Q_y (\tau|x)\). Using QR one can obtain richer
characterizations of the relationships between dependent and independent
variables, by accounting for otherwise unobserved heterogeneity.

A relatively recent development in the literature has focused on
extending quantile regressions analysis to include individual fixed
effects in the framework of panel data. However, as described in
\citet{neymanscott1948}, and \citet{lancaster2000}, when individual
fixed effects are included in quantile regression analysis it generates
an incidental parameter problem. While many strategies have been
proposed for estimating this type of model (see
\citet{galvao2017quantile} for a brief review), neither has become
standard because of their restrictive assumptions in regards to the
individual effects, the computational complexity, and implementation.

More recently, \citet{mss2019} (MSS hereafter) proposed a methodology
based on a conditional location-scale model similar to the one described
in \citet{he1997} and \citet{zhao2000}, for the estimation of quantile
regressions models for panel data via a method of moments. This method
allows individual fixed effects allowing to have heterogeneous effects
on the entire conditional distribution of the outcome, rather
constraining their effect to be a location shift only as in
\citet{canay2011}, \citet{koenker2004}, and \citet{lamarche2010}.

@@

The rest of the paper is restructured as follows. Section 2 presents the
basic setup of the location-Scale model described in \citet{he1997} and
\citet{zhao2000}, tying the relationship between the standard quantile
regression model, and the location and scale model. It also revisits MSS
methodology, proposing alternative estimators for the standard errors
based on the properties of GMM estimators and the empirical influence
functions. It also shows that FWL theorem can be used to control for
multiple fixed effects. Section 3 presents the results of a small
simulation study and Section 4 illustrates the application of the
proposed methods with one empirical example. Seccion 5 concludes.

@@

Quantile regressions are used to identify relationships between the
explanatory variables \(x\) and the conditional quantiles of the
dependent variable \(Q_y(\tau|X)\). This relationship is commonly
assumed to follow a linear functional form:

\begin{equation}\phantomsection\label{eq-eq1}{Q_y(\tau|X) =X\beta(\tau)
}\end{equation}

This allows for the effect of \(X\) on \(Y\) to vary across all
\(\tau\). This formulation can also be related to a random coefficient
model, where all coefficients are assumed to be some nonlinear function
of \(\tau\), where \(\tau\) follows a random uniform distribution.

@@

\begin{equation}\phantomsection\label{eq-eq2}{Q_y(\tau|X) =X\beta+X\gamma(\tau)
}\end{equation}

Here, the location parameters \(\beta\) are typically identified using a
linear regression model (as in \citet{mss2019}), or a median regression
(as in \citet{zhao2000}), and the scale parameters \(\gamma(\tau)\) can
be estimated using standard approaches.

@@

\begin{equation}\phantomsection\label{eq-eq5}{Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
}\end{equation}

In this setup, the traditional quantile coefficients are identified as
the location model coefficients, plus the scale model coefficients
moderated by the \(\tau_{th}\) unconditional quantile of the
standardized error \(\varepsilon\). For simplicity we will use
\(q(\tau)\) to denote \(Q_\varepsilon(\tau)\) in the rest of the paper.

\begin{equation}\phantomsection\label{eq-eq6}{\beta(\tau) = \beta + q(\tau) \times \gamma 
}\end{equation}

While this specification imposes a strong assumption on the DGP, it has
two advantages over the standard quantile regression model. First,
because the location and scale model can be identified globally, with
only a single paramater (\(q(\tau)\)) requiring local estimation, this
estimation approach would be more efficient than the standard quantile
regression model \citep{zhao2000}. Second, under the assumption that
\(X\gamma\) is strictly possitive, the model would produce quantile
coefficients that do not cross.

Following MSS, the quantile regression model defined by
Equation~\ref{eq-eq5} can be estimated using a method of moments
approach. And while its possible to identify all coefficients
(\(\beta,\gamma, q(\tau)\)) simultaneously, we describe and use the
implementation approach advocated by MSS which identifies each set of
coefficients separately.

First, the location model can be estimated using a standard linear
regression model, where the dependent variable is the outcome \(y\), and
the independent variables are the explanatory variables \(X\) (including
a constant) with an error \(u\), which is by definition heteroskedastic.
In this case, the location model coefficients are identified under the
following condition:

@@

\begin{equation}\phantomsection\label{eq-eq8}{\begin{aligned}
  |\nu_i| &=x_i'\gamma+\omega_i \\
   E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
  \end{aligned}
}\end{equation}

Third, given the location and scale coefficients, the \(\tau_{th}\)
quantile of the error \(\varepsilon\) can be estimated using the
following condition:

\begin{equation}\phantomsection\label{eq-eq9}{\begin{aligned}
  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q(\tau)) \geq y_i \right) - \tau \right] &=0  \\
  E\left[  \mathbb{1}\left(   q(\tau) \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
  \end{aligned}
}\end{equation}

Where one identifies the quantile of the error \(\varepsilon\) using
standardized errors \(\frac{y_i-x_i'\beta}{x_i'\gamma}\), or by finding
the values that identify the overall quantile coefficients
\(\beta(\tau)=\beta + \gamma q(\tau)\). Afterwords, the conditional
quantile coefficients is simply defined as the combination of the
location and scale coefficients.

@@

\begin{equation}\phantomsection\label{eq-eq10}{\begin{aligned}
  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
  E\left[  \mathbb{1}\left(   q(\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
  &=E[h_{3,i}]=0 
  \end{aligned}
}\end{equation}

@@

Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'\) the set of
coefficients that are identified by the modement conditions in
Equation~\ref{eq-eq10}, a just identified model. And the function
\(h_i\) is a vector function that stacks all the moments at the
individual level described in Equation~\ref{eq-eq10}. Then
\(\hat\theta\) follows a normal distribution with mean \(\theta\) and
variance-covariance matrix \(V(\theta)\) that is estimated as:

@@

In this framework, the quantile regression coefficients, a combination
of the location-scale-quantile estimates, will follow a normal
distribution with mean \(\beta(\tau) = \beta+\gamma q(\tau)\) and
variance-covariance matrix equal to:

@@

\begin{equation}\phantomsection\label{eq-eqqtile}{\Xi = [ I(k), \hat q(\tau) \times I(k), \hat \gamma ]
}\end{equation}

@@

\begin{equation}\phantomsection\label{eq-ifs}{\begin{aligned}
\lambda_i(\theta)&=
  \begin{bmatrix}
  \lambda_{i}(\beta) \\
  \lambda_{i}(\gamma) \\
  \lambda_{i}(q(\tau)) 
  \end{bmatrix} \\
\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
\lambda_{i}(q(\tau))&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\tau))}
- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
-  q(\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
}\end{equation}

@@

\[\hat{V}_{robust}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\tau))' \\
 \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\tau))' \\
 \sum \lambda_i(q(\tau)) \lambda_i(\beta)' & \sum \lambda_i(q(\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\tau)) \lambda_i(q(\tau))' 
  \end{pmatrix}
\]

@@

\[\hat{V}_{clustered}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
  \end{pmatrix}
\]

@@

\[\begin{aligned}
\tilde \lambda_{1,i}&=\tilde \lambda_{2,i}=N (X'X)^{-1}  x_i ( x_i'\gamma) \\  
\tilde \lambda_{3,i}&=x_i' \gamma  \\
 \psi_1 &= \varepsilon_i \\
 \psi_2 &= \tilde \varepsilon_i -1 \\
 \psi_3 &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
-  q(\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
\]

@@

\[\hat{V}_{gls}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{11} \hat\Omega_{13} \\
 \hat\sigma_{21} \hat\Omega_{21} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{21} \hat\Omega_{23} \\
 \hat\sigma_{31} \hat\Omega_{31} & \hat\sigma_{32} \hat\Omega_{32} & \hat\sigma_{33} \hat\Omega_{33}
  \end{pmatrix}
\]

@@

\[\begin{aligned}
\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \psi_{i} \psi_{j}
\end{aligned}
\]

@@

Similar to the findings in MSS, we find that the estimator presents a
bias when the sample is small (\(N=500\)), but this bias shrinks as the
sample sizes increases. As MSS describes, the bias seems to be
proportional to the sample size, or more precisely to \(N/N_{g1}\) and
\(N/N_{g2}\), where \(N_{g1}\) and \(N_{g2}\) are the average number of
observations per group. Interestingly, the bias-corrected estimator
presents an almost zero bias, even when the samples are small (about 10
observations per sub-group). Also replicating the results of MSS,
despite bias reduction obtained using the JKC estimator, the standard
errors and mean squared error (MSE) are larger than without correction.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}@{}}
\caption{Bias, Simulated Standard error, and Mean Squared
Error}\label{tbl-sim1}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
N = 500
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Bias
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sim SE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
N = 1000
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Bias
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sim SE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MSE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
N = 500
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Bias
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sim SE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
N = 1000
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Bias
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sim SE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MSE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
q25 & & & & q25 & & & \\
~mmqreg & 0.104 & 0.247 & 0.072 & ~mmqreg & 0.050 & 0.173 & 0.032 \\
~jkc & 0.008 & 0.297 & 0.088 & ~jkc & -0.001 & 0.191 & 0.036 \\
q75 & & & & q75 & & & \\
~mmqreg & -0.091 & 0.251 & 0.071 & ~mmqreg & -0.044 & 0.176 & 0.033 \\
~jkc & 0.002 & 0.303 & 0.092 & ~jkc & 0.006 & 0.195 & 0.038 \\
\textbf{N = 2000} & \textbf{Bias} & \textbf{Sim SE} & \textbf{MSE} &
\textbf{N = 4000} & \textbf{Bias} & \textbf{Sim SE} & \textbf{MSE} \\
q25 & & & & q25 & & & \\
~mmqreg & 0.025 & 0.122 & 0.016 & ~mmqreg & 0.012 & 0.087 & 0.008 \\
~jkc & 0.003 & 0.129 & 0.017 & ~jkc & 0.000 & 0.089 & 0.008 \\
q75 & & & & q75 & & & \\
~mmqreg & -0.023 & 0.124 & 0.016 & ~mmqreg & -0.011 & 0.087 & 0.008 \\
~jkc & 0.001 & 0.131 & 0.017 & ~jkc & 0.000 & 0.089 & 0.008 \\
\end{longtable}

@@

\begin{longtable}[]{@{}lcccc@{}}
\caption{Heteroskedasticity misspecification and clustered
errors}\label{tbl-sim2}\tabularnewline
\toprule\noalign{}
& Het:q25 & Het:q75 & Clust:q25 & Clust:q75 \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
& Het:q25 & Het:q75 & Clust:q25 & Clust:q75 \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Coefficient & 0.550 & 1.442 & 0.775 & 1.229 \\
SIM\_SE & 0.154 & 0.155 & 0.109 & 0.107 \\
GLS\_SE & 0.476 & 0.451 & 0.288 & 0.221 \\
Robust & 0.140 & 0.139 & 0.087 & 0.088 \\
Cluster & & & 0.097 & 0.097 \\
\end{longtable}

@@

  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1235}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1111}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}@{}}

@@

\[q(y|\tau,x) = x'(\beta + q(\tau) \times \gamma)\]

where \(q(\tau)\) is the \(\tau_{th}\) quantile of the standardized
residual of \(\varepsilon\). This model is identified under the
following conditions:
